Visualizing Contingency Tables

### 2006-12-11 trunk/vcd/paper/Shadings/JCGS.Rnw
incorporated changes for JCGS shadings paper
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@625 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")}
\citep[\mbox{\url{http://www.R-project.org/}}]{vcd:R:2006} and the packages
\pkg{vcd}~\Sexpr{packageDescription("vcd")$Version} \citep{vcd:Meyer+Zeileis+Hornik:2006},
{\pkg{MASS}~\Sexpr{packageDescription("MASS")$Version}} \citep[see][]{vcd:Venables+Ripley:2002},
{\pkg{grid}~{\Sexpr{packageDescription("grid")$Version}}} \citep[see][]{vcd:Murrell:2002} and
{\pkg{colorspace}~{\Sexpr{packageDescription("colorspace")$Version}}} \citep{vcd:Ihaka:2004}.

>>>>

\section*{Acknowledgements}

We are thankful to Paul Murrell and Ross Ihaka---for providing tools, insights
and feedback that helped to derive the results presented in this paper---and to
two anonymous referees and editor Luke Tierney---for valuable comments and suggestions
that lead to a substantial improvement of the paper.

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")}
\citep[\mbox{\url{http://www.R-project.org/}}]{vcd:R:2006} and the packages
\pkg{vcd}~\Sexpr{packageDescription("vcd")$Version} \citep{vcd:Meyer+Zeileis+Hornik:2006},
{\pkg{MASS}~\Sexpr{packageDescription("MASS")$Version}} \citep[see][]{vcd:Venables+Ripley:2002},
{\pkg{grid}~{\Sexpr{packageDescription("grid")$Version}}} \citep[see][]{vcd:Murrell:2002} and
{\pkg{colorspace}~{\Sexpr{packageDescription("colorspace")$Version}}} \citep{vcd:Ihaka:2004}.
A vignette that demonstrates how all empirical examples can exactly be reproduced by the reader
in \proglang{R} is provided in the package \pkg{vcd}, see
\code{vignette("residual-shadings", package = "vcd")}
